%=============================================================================
% Acknowledgments
% Copyright (c) 2018. Lester James V. Miranda
%
% This file is part of thesis-manuscript.
%
% thesis-mansucript is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% thesis-manuscript is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with thesis-manuscript.  If not, see <http://www.gnu.org/licenses/>.
%
% Created by: Lester James V. Miranda <ljvmiranda@gmail.com>
%=============================================================================

\begin{quote}
{\itshape
Ithaka gave you the marvelous journey.\\
Without her you would not have set out.\\
}
- \textsc{Ithaka}, by C.P. Cavafy
\end{quote}

\par The excerpt above is from the poem, Ithaka, which I kept saved in my phone
as I boarded my plane to Japan. Now, as Odysseus was, I am going home.  The
past two years has been one of the most enriching and productive years of my
life: I have learned about my chosen craft, met different people, and seen new
places. Studying in a foreign country has been a good opportunity; there were
challenges, but I wouldn't have overcome them without everyone's help.

\par First I would like to give my utmost gratitude to Dr. Jinglu Hu. I
wouldn't have completed this work without his unwavering support and guidance.
His breadth of knowledge in the field and his care for us students are traits
that I hope to emulate in the future.

\par I would also like to thank Dr. Yves Lepage and Dr. Mizuho Iwaihara for
their helpful comments in improving this work. Their advice and questions
helped me polish my research. I also extend this gratitude to all the
professors I took classes from in Waseda University: it has been an honor to
learn from you.

\par I would also like to express my gratitude to the Japanese Government for
providing me the Monbukagakusho (MEXT) Scholarship. Without your generous
scholarship, I wouldn't even be here.

\par Next, I would like to thank my friends for all their support and
companionship; your names are too many to fit this single page.  I never felt
alone even if I am the only Filipino in IPS. Thank you for extending
yourselves to a strange foreigner. It has been a pleasure learning from
different cultures and you have all represented your countries well.

\par I would like to thank Anna, for the midnight calls and morning messages.
For listening through my ramblings on proteins and their functions.  For the
love I felt a thousand miles away.

\par I would like to thank my parents, Larry and Joan, for everything. For
encouraging me to go on this journey, and for carrying me when things get
rough. I dedicate this work for both of you.

\par And lastly, I would like to thank God for this grace-filled journey.

\vspace{5ex}
\textit{Maraming salamat! Padayon!}
