%=============================================================================
% Preface
% Copyright (c) 2018. Lester James V. Miranda
%
% This file is part of thesis-manuscript.
%
% thesis-mansucript is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% thesis-manuscript is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with thesis-manuscript.  If not, see <http://www.gnu.org/licenses/>.
%
% Created by: Lester James V. Miranda <ljvmiranda@gmail.com>
%=============================================================================

\par Before you lies the work, ``\ttitle.'' It was written to fulfill the
requirements of the degree, Master of Engineering, at Waseda University. I
started formulating the research questions back in April 2017 and finished
writing this manuscript by June 2018. The research process was challenging yet
exciting. I never had any background in biology two years ago, but I did have
sufficient knowledge in machine learning. Fast-forward today, I can confidently
say that I now know more about proteins\textemdash the \textit{stuff} that
enables our survival.

\par Several parts of this work were
accepted in different academic conferences and symposia. The material in
Chapter \ref{SDAEChapter} can be found in:

\begin{itemize}
    \item \textbf{L. J. V. Miranda} and J. Hu, ``A Deep Learning Approach based
    on Stacked Denoising Autoencoders for Protein Function Prediction,'' in
    \textit{Proceedings of the 42nd IEEE Computer Society Signature Conference
    on Computers, Software, and Applications}, IEEE, July 2018. Note: In press.
    \item \textbf{L. J. V. Miranda} and  J. Hu, ``Feature Extraction using Stacked
    Denoising Autoencoders for Protein Function Prediction,'' in \textit{Proceedings of
    the 11th International Collaboration Symposium on Information, Production,
    and Systems}, November 2017.
\end{itemize}

\par Finally, the material in Chapter \ref{SelectiveChapter} can be found in:

\begin{itemize}
    \item \textbf{L. J. V. Miranda} and J. Hu, ``Feature Extraction using a
    Mutually-Competitive Autoencoder for Protein Function Prediction,'' in
    \textit{Proceedings of the IEEE International Conference on System, Man,
    and Cybernetics}, IEEE, October 2018. Note: In press.
\end{itemize}

Synthesizing two seemingly-unconnected fields, Biology and Computer Science,
has been one of the most rewarding journeys I've undertaken. I discovered new
concepts, and developed a profound appreciation to life. I hope that you'll
feel the same sense of wonder as I did by reading through this work.

\vspace*{4ex}
\begin{flushright}
    \textsc{LJ V. Miranda}\\
    Fukuoka, Japan, June 2018
\end{flushright}
